### 2017-05-13 paper/evaluation.tex
pass on table

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\blankentry}{\entry{-}{-}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{5pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost} $ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%

@@

\bottomrule%
\end{tabular}
\caption{\Fix{Tabela de eficiencia e flakiness}}
\label{tab:rq6-table}
\end{figure*}

>>>>

%% Table header macros
% $\Uparrow_\text{speed}$
\newcommand{\subcolA}{$\text{speedup}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\blankentry}{\entry{-}{-}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1 & #2}

\begin{figure*}[t]  
\centering
\small
\setlength{\tabcolsep}{3pt}
\begin{tabular}{l|rr|rr|rr|rr|rr|rr}
\toprule
\multirow{2}{*}{\emph{Subject (module)}} & \multicolumn{2}{c|}{\emph{\Seq}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T$ & $\mathit{N}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%

@@

\bottomrule%
\end{tabular}
\caption{Speedup versus Flakiness (\subcolB). Configuration
  \emph{\Seq{}} denotes the comparison baseline, which runs tests
  sequentially.  Columns $T$ and $N$ indicate time and number of
  tests, respectively.  Other columns show speedup and percentage of
  failing tests in different configurations, compared to
  \emph{\Seq{}}.\Mar{Can you please add name of module for all subjects?}}
\label{tab:rq6-table}
\end{figure*}
